\subsubsection{30-04-2024}
Attendees: Sidharth Shanmugam, Paul Mitchell, Ben Henson

Agenda:

\begin{itemize}
    \item Discussed final report structuring.
    \begin{itemize}
        \item I proposed my high-level report structure plan, with section names and overall information as to what content goes in each section.
        \item Received invaluable feedback and now have a better idea of how I will be writing the final report.
    \end{itemize}

    \item Final viva presentation.
    \begin{itemize}
        \item Ben suggested I prepare the demonstration presentation before writing the final report. Paul and Ben also suggested I host a seminar regarding my project, presenting to the ISA researchers :).
        \item By preparing the presentation before writing the final report, I will have a better idea of report structuring. And by presenting a seminar, I will gain experience for the viva.
    \end{itemize}
\end{itemize}

Actionable Items:

\begin{itemize}
    \item Prepare presentation.
    \begin{itemize}
        \item I will be preparing an initial draft of a presentation that I could use for my viva, and could also use for a seminar. Although I am quite nervous about presenting my project, as an inexperienced MEng student, to a panel of extremely experienced researchers, Ben and Paul have reassured me that it would not be as bad as I'm portraying it to be.
        \item I'll be discussing this for the next supervision meeting, hopefully with an initial draft at hand.
    \end{itemize}

    \item Carry on writing the final report.
    \begin{itemize}
        \item One of the postdocs at the ISA suggested I give myself a day or two's break after writing the final report so that I can clear my mind, such that when I read it again, I will be able to find faults more easily.
        \item I will aim to finish writing the report some time in advance to allow as much time as possible for Ben to review my section drafts and for me to take a break before reading it again.
    \end{itemize}
\end{itemize}
